### 2012-09-24 paper_sean/hyperneat.tex
Fixed comitted mis-merge as I thought best given the commit history.

% !TEX root =main.tex
HyperNEAT is a neuroevolution method that evolves artificial neuron networks (ANNs) using evolutionary algorithms.
HyperNEAT has shown to evolve large neural networks that represent many features present in brains such as repetitions and regularities \cite{stanley2002evolving}. 
This encoding has previously been applied for gait-learning \cite{yos:clune} and for evolving 2-D and 3-D objects \cite{clune:lipson20113d} and has been successful in displaying complex, natural characteristics such as symmetries and repetition of themes often found in nature.

>>>>

% !TEX root =main.tex
HyperNEAT is an algorithm for evolving artificial neural networks (ANNs)~\cite{stanley2002evolving}.
